DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-26 ase2017/paper.tex
added experimental setup.

>>>>

%-----------------------------------
\subsection{Experimental Setup}
\label{experimental-setup}
%-----------------------------------

For all evaluated benchmarks, the signal input range lies between $-1$ and $1$, and the implementation used for the integer part is $8$ bits, and for fractional part is also $8$ bits.
%
All experiments with \tool v$1$.$0$.$0$  were conducted on an otherwise idle Intel Core i$7-2600$ 
$3.40$ GHz processor, with $24$ GB of RAM, running Ubuntu $64$-bits.
